Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-06-04 analysis/paper/paper.Rmd
Escape `NA` in text

All authors agreed on the evaluation of the data availability of all five articles that were scored by each author (Figure \@ref(fig:irCriteria)A) but one of the authors rated one article as `NA` or no computational methods used rather than zero as with the other four authors (Figure \@ref(fig:irCriteria)B), giving the inter-rater percent agreement a score of 100% with the `NA value dropped from the code availability.
Fleiss' Kappa was not able to be calculated for code or data availability due to 100% agreement of a score of '0', converted to '1' for the analysis.

>>>>

All authors agreed on the evaluation of the data availability of all five articles that were scored by each author (Figure \@ref(fig:irCriteria)A) but one of the authors rated one article as `NA` or no computational methods used rather than zero as with the other four authors (Figure \@ref(fig:irCriteria)B), giving the inter-rater percent agreement a score of 100% with the \`NA value dropped from the code availability.
Fleiss' Kappa was not able to be calculated for code or data availability due to 100% agreement of a score of '0', converted to '1' for the analysis.
